%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\usepackage[scaled]{helvet}
\usepackage[T1]{fontenc}
\renewcommand\familydefault{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-12pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{p{0.70\textwidth}@{\extracolsep{\fill}}r}
		\small\textbf{#1} & {\small #2} \\[-2pt]
		{\small#3} & {\small #4} \\
	\end{tabular*}\vspace{1pt}
}

\newcommand{\resumeChess}[6]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & {\small #2} \\
		{\small#3} & {\small #4} \\
		{\small#5} & {\small #6} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeCertificate}[2]{
	\vspace{-2pt}\item
	{\small #1} \hfill {\small #2} \vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		{\small#1} & {\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{1pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt, parsep=0pt, topsep=3pt, partopsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=2pt, parsep=0pt, topsep=2pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING----------
	\begin{center}
		\textbf{\Large \scshape Henry Nguyen} \\ \vspace{1pt}
		\small San Jose, CA $|$ (206) 751-6618 $|$ \href{mailto:henrynguyen.vp@gmail.com}{henrynguyen.vp@gmail.com} \\
		\small LinkedIn: \href{https://linkedin.com/in/henrynguyen-vp}{linkedin.com/in/henrynguyen-vp} $|$
		GitHub: \href{https://github.com/HenryNVP}{github.com/HenryNVP}
	\end{center}
	
	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{\textit{Master of Science in Artificial Intelligence}}{\textit{Exp. May 2026}}
	{San Jose State University}{San Jose, CA}
	\vspace{-4pt}
	\resumeItemListStart
	\resumeItem{Coursework: AI \& Data Engineering, Machine Learning, Deep Learning, Intelligent Autonomous Systems, Data Mining}
	\resumeItemListEnd
	\vspace{2pt}
	\resumeSubheading
	{\textit{Bachelor of Engineering in Mechatronic Engineering}}{\textit{Apr. 2023}}
	{Ho Chi Minh City University of Technology}{Vietnam}
	\resumeSubHeadingListEnd

	%-----------TECHNICAL SKILLS-----------
	\section{Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
		\small{
			\item{
				\textbf{AI \& Agents}{: LLMs, LangGraph, RAG, Vector DBs, LangChain, Agentic AI, Reasoning techniques (Chain-of-Thought).} \\
				\textbf{Machine Learning \& Deep Learning}{: PyTorch, ONNX, TensorRT, Scikit-learn, CNNs, Transformers, Recommender systems.} \\
				\textbf{Robotics \& Autonomous Systems}{: ROS2, LiDAR-Camera Fusion, SLAM, Control systems, Autonomous driving pipelines.} \\
				\textbf{Software \& Deployment}{: Python, FastAPI, Microservices, Git, Docker, Edge \& mobile AI deployment.}
			}
		}
	\end{itemize}

	%-----------FEATURED AI PROJECTS-----------
	\section{Featured AI Projects}
	\resumeSubHeadingListStart
	
	\resumeProjectHeading
	{\textbf{SAM-E: Multi-Agent Enrollment Assistant} $|$ \emph{GenAI, RAG, LangGraph, Docker, FastAPI}}{}
	\resumeItemListStart
	\resumeItem{Architected a microservices-based agentic system with three services (Agent, RAG, Enrollment Engine) using \textbf{Docker Compose} and \textbf{LangGraph} to route user intents to specialized tools.}
	\resumeItem{Developed a retrieval pipeline using \textbf{pgvector} to support academic queries, with planned integration of a \textbf{Neo4j} knowledge graph; demonstrated functionality via \textbf{FastAPI}, \textbf{JWT authentication}, and \textbf{Prometheus} metrics.}
	\resumeItemListEnd
	
	\resumeProjectHeading
	{\textbf{AI Tutor: RAG-Powered Learning Platform} $|$ \emph{GenAI, RAG, MCP, FastAPI, OpenAI Agents SDK}}{}
	\resumeItemListStart
	\resumeItem{Built a full-stack multi-agent educational system that ingests documents to generate cited answers, adaptive quizzes, and lesson notes via a source-filtered \textbf{RAG} pipeline using \textbf{ChromaDB}.}
	\resumeItem{Implemented an \textbf{MCP server} and secure Python execution with \textbf{FastAPI} backend, enabling structured tool use, real-time data visualization from CSVs, and adaptive learning features that track student progress.}
	\resumeItemListEnd
	
	\resumeProjectHeading
	{\textbf{ROS2 BEV-Fusion: Real-Time 3D Perception} $|$ \emph{Python, ROS2, TensorRT, CUDA, Jetson, Edge AI}}{}
	\resumeItemListStart
	\resumeItem{Developed an optimized \textbf{BEVFusion} 3D perception pipeline for multi-camera and LiDAR fusion, validated on NuScenes and deployed as a modular \textbf{ROS2} package.}
	\resumeItem{Optimized end-to-end inference with \textbf{TensorRT} and quantization, achieving $\sim$7 FPS for the full BEVFusion pipeline on Jetson Orin Nano and publishing \textbf{ROS2} detection outputs with latency metrics.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	%-----------ADDITIONAL PROJECTS-----------
	\section{Additional Projects}
	\resumeSubHeadingListStart
	\resumeItem{\textbf{FastViT Mobile Optimization:} Optimized Vision Transformers using \textbf{Performer attention} (O(N) complexity) and knowledge distillation, achieving \textbf{90.1\% accuracy} @ \textbf{43ms} on Android with stage freezing for transfer learning.}
	\resumeItem{\textbf{3D Object Detection Pipeline:} Built a 3D object detection inference pipeline using \textbf{MMDetection3D} (PointPillars, SECOND, CenterPoint) for KITTI and nuScenes, focusing on model evaluation, visualization, and deployment analysis.}
	\resumeItem{\textbf{Image Classification:} Developed a flexible image classification pipeline with \textbf{timm}, enabling YAML-based training and benchmarking of CNN and ViT architectures on the Oxford-IIIT Pet dataset.}
	\resumeItem{\textbf{Anime RecSys:} Benchmarked \textbf{Two-Tower} vs. NeuMF architectures with multiple objectives (MSE, ApproxNDCG); deployed best model via \textbf{FastAPI} with sub-50ms latency.}
	\resumeItem{\textbf{Client Web Projects:} Built and maintained \textbf{WordPress} websites with automated booking tools; improved SEO and performance, increasing client inquiries.}
	\resumeSubHeadingListEnd
	
	%-----------PROFESSIONAL EXPERIENCE-----------
	\section{Professional Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{\textit{Software Engineer (Automotive Systems)}}{Jun. 2023 -- Dec. 2023}
	{Bosch Global Software Technologies}{Ho Chi Minh, Vietnam}
	\resumeItemListStart
	\resumeItem{Led integration testing for the Electronic Stability Program (ESP) across 10+ projects, ensuring ISO-standard compliance for safety-critical automotive software.}
	\resumeItem{Collaborated with 5+ cross-functional teams to debug Hardware-in-the-Loop (HIL) failures, reducing defect resolution time by streamlining the error-reporting workflow.}
	\resumeItemListEnd
	
	\resumeSubheading
	{\textit{Undergraduate Researcher}}{Aug. 2022 -- Dec. 2022}
	{Mechatronics Lab, HCMUT}{Ho Chi Minh, Vietnam}
	\resumeItemListStart
	\resumeItem{Designed an adaptive 3-finger robotic gripper (+200\% payload capacity) and developed the C++ control stack for a 5-axis manipulator to execute automated pick-and-place tasks.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
\end{document}

